\LARGE \bf A Teachable Robotic Agent for Children Learning Handwriting, Capable of Simulated Handwriting Itself

### 2014-12-02 main.tex
Improve conciceness in sections 4 and 5

In addition to constituting a technically novel system, the presented teachable
robotic agent represents a tool which may be used for investigating social and
pedagogical research questions. For example, one such question is what impact the addition of
such a teachable robotic agent would have on the outcomes of a typical
handwriting intervention. 
%Preliminary studies has been conducted to evaluate 
%the feasibility of the system as a technical tool for such investigations.

@@

The interaction context which has been developed as a framework for addressing
relevant research questions is one where participants are asked to improve the robot's
handwriting by correcting its letters. Figure~\ref{fig:pilotInteraction}
illustrates an example interaction sequence between the participant and the
robot which consists of the following stages:

@@

%To allow the system to take input from the user on which words to draw,
%fiducial markers were placed on cards which were detectable by a
%previously-developed ROS node processing a camera stream. A node which
%processed the fiducial markers detected was then created to convert the card
%detected into an appropriate message for the controller.

@@

\subsection{Outcomes of Preliminary Studies}

Preliminary studies at two schools in the Geneva area, involving more than 50 children, 
have been conducted to evaluate the feasibility and technical soundness of the 
interaction system proposed.

@@

The study at the second school involved 21 french-speaking students aged 7-8 years: 7 children
interacted with the robot individually and 7 sessions included the remaining
14 students interacting with the robot in pairs. The duration of the sessions
was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3). 
Initial parameters were drawn from a range purposely chosen to generate shapes 
for letters 'e' and 's' which would elicit correction. For the other letters, 
parameters were fixed, generating shapes which some groups chose to correct 
(e.g. 13/14 for 'n' and 2/14 for 'c').

The following conclusions were successfully drawn about the system as a result
of the study at the second school.

    \textbf{The simulated robotic writing was believed by the children in all
    cases.} There were, at times, 
    % * <deanna.m.hood@gmail.com> 2014-09-05T11:59:03.640Z:
    %
    % how many
    %
    questions about the robot's writing method at the beginning of the interaction,
    but when advised that the robot ``tells the tablet what it wants to write,''
    this was accepted by the children. To allow the children an opportunity to
    express doubt in the robot's ability to write without explicitly asking them if
    the robot was pretending, the children were asked if they believed that the
    robot would be able to write its name, \emph{{\sc nao}} which had not previously been
    demonstrated. It was reasoned that this would prompt the children to question
    the point of the robot actually \emph{writing} if they had any suspicion that
    the robot was pretending, but this was never the case. In the event where the
    robot's writing was not correctly synchronised with the tablet, this did not affect the
    response of the child. If older children participate in the interaction study --
    which may be likely as children with lasting handwriting difficulties are included
    as participants -- it may become more important to invest time into the
    believability of the robot's writing scheme. However, for 6-8 year olds the
    proposed setup has been proven viable.

    \textbf{The children were engaged in teaching the robot.} % * <deanna.m.hood@gmail.com> 2014-09-05T09:54:48.069Z:
    %
    % maybe this is too strong as a 'conclusion' and should just be an observation. plus what does this even mean.. the child walking around the room was 'engaged' too...?
    %
    An average of 10.9 demonstration letters (SD = 4.4) were
    provided to the robot for each session during the interaction.
    In 9 out of the 14 sessions (64\%), the robot received demonstration letters
    \emph{after} reaching the test stage of the interaction. The participants'
    teaching after the test word had been written and evaluated -- the only
    purposefully imposed external motivation -- may suggest that by that time
    the participants had become intrinsically motivated to engage in the
    interaction.% * <deanna.m.hood@gmail.com> 2014-09-05T10:30:45.293Z:
    %
    % I guess it could have also come from us sitting there watching them
    %

    \textbf{All children believed that the robot was learning and that
        they were the ones teaching it.} This was concluded from the responses
        when the children were asked directly. This is in contrast to a prior
        feasibility study for a version of the interaction which only allowed
        for touch-based feedback, not user demonstrations, in which three of the
        seven adult participants did not feel that it was their input which
        helped the robot improve.
        % * <deanna.m.hood@gmail.com> 2014-09-05T09:46:49.117Z:
    %
    % probably can't just casually mention this study without going into more detail...
    %

@@

    \textbf{The system has been validated as a technically sound
        autonomous interaction.} The interaction setup including the teachable
        robotic agent withstood the interaction for a total of 160 minutes. During this
        time the robot wrote 335 letters, 152 of which in response to
        demonstrations received from the 21 children. During this time, technical 
	intervention was only required for the three instances that the robot fell 
	later in the day. Otherwise, the technical components of the system operated 
	autonomously and as expected over the sessions.
        %, with only verbal interaction for prompting being required from an observing researcher.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Towards Long-term Interventions}\label{sec:futureWork}
%why is this title going into the margins....

A conclusion drawn in~\cite{Hoy2011} is that any 
handwriting intervention studies considered in the systematic review which involved 
fewer than two practice sessions per week and fewer than a total of 20 practice 
sessions, including homework, were not found to demonstrate effective results. This 
highlights the necessity to engage students in an interaction which will be sustainable
 over the long-term in order to answer 
research questions which involve the measurement of learning gains. 
Several challenges are raised in developing such long-term capabilities for the system,
 from both technical and sociological points of view. %not sure this makes sense

@@

In the scope of open technical questions for enabling long-term interaction, it remains to be seen how shape models
for letters might be generated which capture the full range of mistakes typical
of children learning handwriting. This includes extending the current system capable of
incorporating internal proportion and global deformation errors to one which can
also generate missing subparts of the letter, or break the letter down into
primitive strokes, for example. While it is expected that incorporating a
database of letters drawn by children into the shape modeling process would
facilitate this, the current system has conceptual -- a PCA-only approach can not
generate or learn a different shape topology -- and technical -- no support is currently implemented for
multi-stroke shapes -- limitations which would need to be overcome.

@@

With some of the challenges towards an engaging long-term handwriting intervention 
with the teachable robotic partner addressed, further steps can be made towards 
answering the central question of what impact to the outcomes of interventions the 
addition of such a teachable robotic agent would have, including the effect on the 
participants' self-esteem, motivation, and learning gains. % does it impact the
%motivation of the participants, their self-esteem, and/or the learning gains
%that they experience? We are currently considering running a long-term study
%that would provide better evidences to answer these questions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Anonymized for double-blind review
%\section*{Acknowledgments}

%This research was supported by the Swiss National Science Foundation through the
%National Centre of Competence in Research Robotics.

>>>>

In addition to constituting a technically novel system, the presented teachable
robotic agent represents a tool which may be used for investigating social and
pedagogical research questions. For example, one such question is what impact the addition of
such a teachable robotic agent would have on the outcomes of a typical
handwriting intervention. 
Preliminary studies at two schools in the Geneva area, involving more than 50 children, 
have been conducted to evaluate the feasibility and technical soundness of the 
interaction system proposed as a tool for such investigations.

@@

%The interaction context which has been developed as a framework for addressing
%relevant research questions is 
%Participants are asked to improve the robot's
%handwriting by correcting the letters it writes on the tablet. 
Figure~\ref{fig:pilotInteraction}
illustrates an example interaction sequence between the participant and the
robot which consists of the following stages:

@@

@@

\subsection{Outcomes of Preliminary Study 1}

@@

\subsection{Outcomes of Preliminary Study 2}
The study at the second school involved 21 french-speaking students aged 7-8 years. 7 children
interacted with the robot individually and 7 sessions included the remaining
14 students interacting with the robot in pairs.
Initial parameters were drawn from a range purposely chosen to generate shapes 
for letters 'e' and 's' which would elicit correction. For the other letters, 
parameters were fixed, generating shapes which some groups chose to correct 
(e.g. 13/14 for 'n' and 2/14 for 'c'). The duration of the sessions
was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3).

%The following conclusions were successfully drawn about the system as a result
%of the study at the second school.

It has been concluded following the second study that the system has 
been validated as a technically sound autonomous interaction. 
The interaction setup including the teachable
robotic agent withstood the interaction which lasted for a total of 160 minutes. 
During this time the robot wrote 335 letters, 152 of which in response to
demonstrations received from the 21 children. Technical 
intervention was only required for the three instances that the robot fell 
later in the day. Otherwise, the technical components of the system operated 
autonomously and as expected over the sessions.

Furthermore, no child indicated that they did not attribute the writing
to the robot. There were, at times, 
    questions about the robot's writing method at the beginning of the interaction,
    but when advised that the robot ``tells the tablet what it wants to write,''
    this was accepted by the children. 
%     To allow the children an opportunity to
%     express doubt in the robot's ability to write without explicitly asking them if
%     the robot was pretending, the children were asked if they believed that the
%     robot would be able to write its name, \emph{{\sc nao}} which had not previously been
%     demonstrated. It was reasoned that this would prompt the children to question
%     the point of the robot actually \emph{writing} if they had any suspicion that
%     the robot was pretending, but this was never the case. 
    On the rare occasion that the
    robot's writing was not correctly synchronised with the tablet, this did
    not appear to influence the children's impression. 
    If older children participate in the interaction study --
    which may be likely as children with lasting handwriting difficulties are included
    as participants -- it may become more important to invest time into the
    believability of the robot's writing scheme. However, for 6-8 year olds the
    proposed setup appears sufficient.

Regarding the engagement of the children in teaching the robot, 
    an average of 10.9 demonstration letters (SD = 4.4) were
    provided to the robot for each session during the interaction.
    In 9 out of the 14 sessions (64\%), the robot received demonstration letters
    \emph{after} reaching the test stage of the interaction. The participants'
    teaching after the test word had been written and evaluated -- the only
    purposefully imposed external motivation -- may suggest that by that time
    the participants had become intrinsically motivated to engage in the
    interaction.

%     \textbf{All children believed that the robot was learning and that
%         they were the ones teaching it.} This was concluded from the responses
%         when the children were asked directly. This is in contrast to a prior
%         feasibility study for a version of the interaction which only allowed
%         for touch-based feedback, not user demonstrations, in which three of the
%         seven adult participants did not feel that it was their input which
%         helped the robot improve.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Towards Long-term Studies}\label{sec:futureWork}
%How to break this section up?

A conclusion drawn in a systematic review handwriting intervention studies \cite{Hoy2011} 
is that any of the studies considered which involved 
fewer than two practice sessions per week and fewer than a total of 20 practice 
sessions, including homework, were not found to demonstrate effective results. This 
highlights the necessity to engage students in an interaction which will be sustainable
 over the long-term if 
research questions which involve the measurement of learning gains are to be addressed. 
Several challenges are raised in developing such long-term capabilities for the system,
 from both technical and sociological points of view. %not sure this makes sense

@@

In the scope of open technical questions for enabling long-term interaction, it remains to be seen how shape models
for letters might be generated which capture the full range of mistakes typical
of children learning handwriting. This includes extending the current system capable of
incorporating internal proportion and global deformation errors to one which can
also generate missing subparts of the letter, or write letters backwards, for example. 
While it is expected that incorporating a
database of letters drawn by children into the shape modeling process would
facilitate this, the current system has conceptual -- a PCA-only approach can not
generate or learn a different shape topology -- and technical -- no support is currently implemented for
multi-stroke shapes -- limitations which would need to be overcome.

@@

With some of these challenges addressed, further steps can be made towards 
answering the overarching question of what impact the 
addition of such a teachable robotic agent would have on handwriting interventions, including the effect on the 
participants' self-esteem, motivation, and learning gains. % does it impact the
%motivation of the participants, their self-esteem, and/or the learning gains
%that they experience? We are currently considering running a long-term study
%that would provide better evidences to answer these questions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Anonymized for double-blind review
\section*{Acknowledgments}

This research was supported by the Swiss National Science Foundation through the
National Centre of Competence in Research Robotics.
